Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-22 paper/main.tex
Proper margins
Added hashing in Tahoe figure and tiny bit of text

% We need this to make it easier to ensure we start chapters on odd pages.
\newcommand{\ensureodd}{
    \newpage
%    \thispagestyle{empty}
    \mbox{}
}

@@

The Tahoe \ac{LAFS} is a system for secure,
distributed data storage. Files are encrypted client side, then
split up, before each part is sent to other nodes in the grid. The integrity and
confidentiality of the files are guaranteed by the algorithms used on the
client, and is independent of the storage servers, which may be operated by
untrusted people. This is defined as \emph{provider-independent security}
\cite{t_tahoe}.

@@

@@

Where?

@@

\subsection(Python C-API)
The Python C-API is the official method of creating C-bindings for Python. The
procedure to do this includes writing entrypoints or wrappers for your C
functions in C. Then, through compiling you can acess your C-libraries and
functions through Python. The drawback with this approach, when faced with an
already existing C-library is that you have to actually write the
wrapper-functions or modify the C-library.

>>>>

% Set equal margins on book style
% \usepackage{layout} % Use \layout to print out the margins (debug)
\usepackage{geometry}
\geometry{bindingoffset=1cm}

@@

The Tahoe \ac{LAFS} is a system for secure,
distributed data storage. Files are encrypted client side, then
split up, before each part is sent to other nodes in the grid, as depicted in
figure \ref{fig:tahoeinsertion}. The integrity and confidentiality of the files
are guaranteed by the algorithms used on the client, and is independent of the
storage servers, which may be operated by untrusted people. This is defined as
\emph{provider-independent security} \cite{t_tahoe}.

@@

The properties of erasure coding can be seen up on as those of recovery in RAID
systems.

@@

% Describe hash trees in further detail?

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashing.pdf}
    \caption{Tahoe-LAFS: Location of hashing}
    \label{fig:tahoehashing}
\end{figure}

As seen in figure \ref{fig:tahoehashing}, the usage of secure hashing is
extensive in Tahoe, and has to be considered as a key part of the functionality.

@@

\subsection{Python C-API}
The Python C-API is the official method of creating C-bindings for Python. The
procedure to do this includes writing entrypoints or wrappers for your C
functions in C. Then, through compiling you can acess your C-libraries and
functions through Python. The drawback with this approach, when faced with an
already existing C-library is that you have to actually write the
wrapper-functions or modify the C-library.
